---
title: "Lecture6"
author: "Deepam Gupta"
date: "1/25/2019"
output: "github_document"
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## File reading in R

Here we are again going to learn about some methods that we can implement in R. If I just write the name of the function without any parantheses and without any arguments I get the description and the code of the function. It is also a cool thing about R.
```{r}
file1 <- "test1.txt"
file2 <- "test2.txt"
file3 <- "test3.txt"
data1 <- read.csv(file1)
data2 <- read.table(file2, header=TRUE, sep="$")
data3 <- read.table(file3)

```
Suppose if we are writing any function with a default arguments, like an add function where I am giving one of the arguments as default. I do not need to give two arguments, I might do well with only one argument
```{r}
add <- function(x, y=1){
  #Sum the two 
  x+y
}
```
Now let use the add function
```{r}
add(3,4)
```
If we use more arguments than are present in the definition of the function, then there will be an error. Similiarly, if I allow the passing of a non integer or a different type 
Now is the time for the next function
```{r}
rescale <- function(x){
  rng <- range(x)
  (x-rng[1])/(rng[2]-rng[1])
}
rescale(1:10)
#rescale(c(1,2,NA,3,4)) will give us an error. This is because it cannot have a range for the NA. Instead we can do a removal of NA, by using the modified function
```
```{r}


rescale2 <- function(x){
  rng <- range(x, na.rm=TRUE)
  (x-rng[1])/(rng[2]-rng[1])
}
rescale2(c(1,2,3,NA,5))
```

```{r}
rescale3 <- function(x, na.rm=TRUE, plot=FALSE) {
 if(na.rm) {
 rng <-range(x, na.rm=na.rm)
 } else {
 rng <-range(x)
 }
 print("Hello")
 answer <- (x - rng[1]) / (rng[2] - rng[1])
 print("is it me you are looking for?")
 if(plot) {
 plot(answer, typ="b", lwd=4)
 }
 print("I can see it in ...")
 return(answer)
}
rescale3(1:10)

```

